Making all equalities equal

### 2021-12-13 paper.lagda.tex
Finished the explain of equalities

% \end{code}
%
% \begin{code}

@@

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
        constructor eq
        field
          ≣-≡-≡ : let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

            in x≣y ≡₃ x≡y

        instance
          ≣-isEquality₂ : IsEquality₂ _≣_
          ≣-isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)

@@

        ≡-≡-≣ : let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
          in transport α₁ (α₂ ∙ α₃)

      module _
        (Eq₂ : Equality {_} {ℓ} {A})
        where

@@

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))

module LeibnizFromPEquality {A : Set} where
  open Equalities {ℓ-zero} {ℓ-suc ℓ-zero}

  _≡p₁_ : A → A → Set₁
  x ≡p₁ y = x ≡p y

  instance
    ≡p₁-isEquality : IsEquality _≡p₁_
    ≡p₁-isEquality = eq λ {x y} → (sym λ i → let
      α : Type₁
      α = p-c {ℓ-zero} {x = x} {y = y} i
      in α)

  leibniz : IsEquality {A = A} _≐_
  leibniz =
    IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)

@@

>>>>

@@

\subsection{Everything is an equality}

In this part, a relation is an equality when it is equal (using a general equality) to a cubical equality.

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
        constructor eq
        field
          ≣-≡-≡ : (x ≣ y) ≡₃ (x ≡₁ y)
\end{code}

With this definition of equality, it is possible to prove that if an equality is equal to a cubical equality,
so it is equal (using the general or cubical equality) to the cubical equality.

\begin{code}
        instance
          ≣-isEquality₂ : IsEquality₂ _≣_
          ≣-isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)

@@

This is the proof that the symmetric definition of equality is also valid.

\begin{code}
        ≡-≡-≣ : (x ≡₁ y) ≡₃ (x ≣ y)
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
          in transport α₁ (α₂ ∙ α₃)
\end{code}

It is possible to proof that a general equality is an equality from this definition:

@@

@@

If there is a proof of the symmetrical equality, so it is also an equality from this definition:

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ :
          (≡-≡-≣ : ∀ {x y} → (x ≡₁ y) ≡₃ (x ≣ y))
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))

\section{Using the definitions}

The best part of defining all of these stuffs is that it is now easy to proof that Leibniz equality is an equality.

\begin{code}
module LeibnizFromPEquality {A : Set} where
  open Equalities {ℓ-zero} {ℓ-suc ℓ-zero}

  _≡p₁_ : A → A → Set₁
  x ≡p₁ y = x ≡p y
\end{code}

I redefined this equality because it must be a set of universe one.
And because of that, I have to prove again that this is an equality:

\begin{code}
  instance
    ≡p₁-isEquality : IsEquality _≡p₁_
    ≡p₁-isEquality = eq λ {x y} → (sym λ i → let
      α : Type₁
      α = p-c {ℓ-zero} {x = x} {y = y} i
      in α)
\end{code}

With just one line of code, it is possible now to prove that Leibniz equality is an equality
from Martin-Löf Equality.

\begin{code}
  leibniz : IsEquality {A = A} _≐_
  leibniz = IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)
\end{code}
